Selective electroporation of the viral envelope

### 2021-04-12 documents/lessons_learned.tex
Fiiine I'll do it numerically
Using a real optimal control software

>>>>

when you build a project, put aside a certain amount of money and time to justify helping future people

At least with mathematics, it seems to generally be easier to find a starting point closer to your desired one than to work it out yourself. If you get stuck trying to massage things into a different representation, look harder for a different formulation.
